Trump vs. Harris: A Data-Driven Forecast modeling the 2024 US Presidential Elections

### 2024-11-04 paper/paper.qmd
Edited intro

The main estimand is the projected support percentage and each candidate's winning probability in terms of state-level victories and Electoral College votes. This paper utilizes linear regression model incorporates numeric value of the credibility of pollsters, number of respondents, poll's recency to estimate the probability of each candidate winning in individual states. The objective is to translate these probabilities into a forecast the overall winner of the election. Our findings reveal a close race, with Trump holding a slight edge in the Electoral College due to projected victories in key swing states, despite Harris maintaining a lead in national popular vote estimates.

>>>>

The main estimand is the projected support percentage and each candidate's winning probability in terms of state-level victories and Electoral College votes. This paper utilizes linear regression model incorporates numeric value of the credibility of pollsters, number of respondents, poll's recency to estimate the probability of each candidate winning in individual states. The objective is to translate these probabilities into a forecast the overall winner of the election. Our findings reveal a close race, with Trump holding a slight edge in both the popular vote and Electoral College due to projected victories in key swing states.
